Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-02-07 src/tex/ms.tex
streamline discussion on Bayes factors and priors

>>>>

\rev{
\subsubsection{Bayesian Evidence and the Influence of Priors}
Our semi-analytical analysis (Section~\ref{sec:results-semianalytical}) employs Bayes factors to quantify the evidence in favor of or against the UV~Threshold Hypothesis that future observations may provide.
%In contrast to frequentist p-value tests, which only assess the likelihood of the null hypothesis, this approach explicitly incorporates the likelihood of the alternative hypothesis.
%However, Bayes factor analysis limits the scope to two competing hypotheses, and it does not estimate posterior probabilities.
}

\rev{
Using the Bayes theorem
%\begin{equation}
%    \label{eq:BayesTheorem}
%    P(H_i|X) = \frac{P(X|H_i)P(H_i)}{P(X)}
%\end{equation}
to estimate posterior probabilities would allow for a more complete assessment by quantifying information gain and integrating prior knowledge into hypothesis testing.
In practice, implementation of a full Bayesian inference is often hindered by the subjectivity of prior distributions.
Here, we thus chose to provide merely a general assessment of the potential evidence yield from future observations.
In essence, we addressed the question: \textit{By how much does a particular observation tip the scale between the UV~Threshold Hypothesis and the null hypothesis?}
}
